Species motif participation provides unique information about species risk of extinction

### 2023-05-11 manuscript/reorder_main_text.tex
Updates from Overleaf

        A middle‐ground approach for simulating secondary extinctions is to use Bayesian networks, which are much more computationally efficient and facilitate the analysis of larger networks than is practical for dynamical models \citep{Eklof2013,Haussler2020}. 
        In this framework, a consumer's probability of extinction depends on the fraction of resources lost ($f = k/n$ for a species with $n$ resources, of which $k$ have gone extinct) and on a baseline probability of extinction ($\pi$) which captures factors affecting the focal species' extinction probability that are not related to the network structure (e.g., disease or stochastic extinction of small populations).
        Importantly, the greater speed of the Bayesian network framework allows us to simulate a range of disturbance severities rather than single species removals as in many previous studies (e.g.,~\citealp[]{Memmott2004,Staniczenko2010,Dunne2004,Cirtwill2022Oikos}).
        Moreover, Bayesian network simulations are less parameter-intensive than dynamical models, meaning that they are less sensitive to assumptions made in the modelling process~\citep{Eklof2013}.

@@

        \subsubsection*{Modelling consumers' risk of secondary extinction}

>>>>

        A middle‐ground approach is to use Bayesian networks, which are much more computationally efficient and facilitate the analysis of larger networks than is practical for dynamical models \citep{Eklof2013,Haussler2020}. 
        In this framework, a consumer's probability of extinction depends on the fraction of resources lost ($f = k/n$ for a species with $n$ resources, of which $k$ have gone extinct) and on a baseline probability of extinction ($\pi$) which capturing factors that are not related to the network structure (e.g., disease or stochastic extinction of small populations).
        Importantly, the greater speed of the Bayesian network framework allows us to simulate a range of disturbance severities rather than single species removals as in many previous studies (e.g.,~\citealp[]{Memmott2004,Staniczenko2010,Dunne2004,Cirtwill2022Oikos}).
        Moreover, Bayesian network simulations are less parameter-intensive than dynamical models and are therefore less sensitive to assumptions made in the modelling process~\citep{Eklof2013}.

@@

        \subsubsection*{Modelling consumers' risk of secondary extinction} [[trimmed down to here]]
